Open Data, Open Source and Open Standards in chemistry - The Blue Obelisk five years on

### 2011-05-12 paper.tex
Combine bioclipse and avogadro paragraphs

Bioclipse~\cite{Spjuth:2007fk} (v2.4 released in Aug 2010) and Avogadro
\cite{WebAvogadro} (v1.0 in Oct 2009) are two examples of such software, based
on the CDK and Open Babel, respectively. Bioclipse is an award-winning
molecular workbench for life sciences with a dynamic plugin architecture, and
which wraps cheminformatics functionality behind user-friendly interfaces and
graphical editors. All functionality in Bioclipse is completely scriptable
using an integrated high-level language called Bioclipse Scripting Language
(BSL), which can be used for scripted research or to automate complex
tasks~\cite{Bioclipse2}. Bioclipse in turn acts as base for other software
such as Brunn~\cite{WebBrunn}, a laboratory information system for
microplate based high-throughput screening. Brunn provides a grahical interface
for handling different plate layouts and dilution series and can automaticly
generate dose response curves and calculate IC$_{50}$-values.

Avogadro is a 3D molecular editor and viewer aimed at preparing
and analysing computational chemistry calculations. An interesting
aspect of both Avogadro and Bioclipse is that they share some developers
with the underlying toolkits and this has driven the development of new
features in the CDK and Open Babel.

>>>>

Bioclipse~\cite{Spjuth:2007fk} (v2.4 released in Aug 2010) and Avogadro
\cite{WebAvogadro} (v1.0 in Oct 2009) are two examples of such software, based
on the CDK and Open Babel, respectively. Bioclipse is an award-winning
molecular workbench for life sciences
which wraps cheminformatics functionality behind user-friendly interfaces and
graphical editors while Avogadro is a 3D molecular editor and viewer aimed at
preparing and analysing computational chemistry calculations. Both
projects have are designed to be extended or scripted by users through
a plugin architective and the provision of scripting support (using
Bioclipse Scripting Language~\cite{Bioclipse2}, or Python in the case
of Avogadro).
An interesting
aspect of both Avogadro and Bioclipse is that they share some developers
with the underlying toolkits and this has driven the development of new
features in the CDK and Open Babel.

Bioclipse in turn acts as base for other software
such as Brunn~\cite{WebBrunn}, a laboratory information system for
microplate based high-throughput screening. Brunn provides a graphical interface
for handling different plate layouts and dilution series and can automaticly
generate dose response curves and calculate IC$_{50}$-values.
